\section{Succinct Representation (SODA 2015, §3.2)}
\label{sec:ere}

The inner layer of every approximate filter is an \emph{Exact Range Emptiness} (ERE)
structure: given a universe $[0, r)$ where $|r| = \lceil \log_2 r \rceil$ denotes the
key length in bits, and a sorted set $S \subset [0, r)$ of $n$ keys, it answers
``$[a, b] \cap S = \emptyset$?'' with zero error.

\subsection{Two-Level Hierarchy}

To achieve the information-theoretic minimum of $n \log_2(r/n) + O(n)$ bits, the
structure divides the universe $[0, r)$ into $n$ equal-sized blocks:

\paragraph{Global level (succinct indexing).}
Two bit-vectors provide $O(1)$ navigation:
\begin{itemize}
  \item $D_1$ (size $n$ bits): $D_1[i] = 1$ if block $i$ contains at least one key.
  \item $D_2$ (size ${\sim}2n$ bits): an Elias--Fano~\citep{elias1974efficient,fano1971number}
    representation of block counts. Each non-empty block $i$ contributes a $1$ followed
    by $n_i$ zeros. A \textsc{Select}$_1$ / \textsc{Rank}$_0$ pair maps any block index
    to its starting position in the data array in $O(1)$ time.
\end{itemize}

\paragraph{Local level (bit-packed suffixes).}
Instead of storing full keys, only the suffix $x \bmod (r/n)$ is stored for each
key~$x$. The suffix length is $W = |r| - \lceil \log_2 n \rceil$ bits. All suffixes are packed into a dense \texttt{uint64} array using bit-shifts,
eliminating per-element overhead.

\subsection{Binary Search in Buckets}

The original SODA~2015 paper suggests a Weak Prefix Search structure (Hollow Z-Fast
Trie) for $O(1)$ worst-case local queries. Our implementation uses binary search on
bit-packed suffixes instead.

With $n$ blocks for $n$ keys, the number of keys per non-empty block follows a Poisson
distribution with $\lambda \approx 1$. In practice: ${\sim}2.24$ keys per non-empty
block on average, and at most ${\sim}12$ keys for $n = 10^6$ in our tests. Binary
searching through ${\sim}12$ packed values is faster and more cache-friendly than
multiple rank/select lookups in a trie.

When ERE is used inside an ARE filter, the fingerprint length $K$ is typically 7--11
bits (Section~\ref{sec:soda}). With suffixes of at most $K$ bits, an entire bucket
occupies a few hundred bytes --- well within L1 cache. This makes the binary search
effectively free compared to any pointer-chasing structure.

\subsection{Space Analysis}

\begin{table}[h]
\centering
\begin{tabular}{@{}lrrr@{}}
\toprule
$|r|$ (key bits) & Suffix bits ($|r| - \log_2 n$) & Metadata & Total BPK \\
\midrule
64   & 44.07  & 3.2 & 47.27  \\
128  & 108.07 & 3.2 & 111.27 \\
256  & 236.07 & 3.2 & 239.27 \\
512  & 492.07 & 3.2 & 495.27 \\
\bottomrule
\end{tabular}
\caption{Measured ERE space with $n = 10^6$ keys. Metadata ($D_1 + D_2$ + rank/select
  indices) is constant at ${\sim}3.2$ BPK.}
\label{tab:ere-space}
\end{table}

Space grows linearly with $|r|$ --- unavoidable for an exact structure, since it must
store the information distinguishing the keys. This linear dependence motivates the
move to approximate range emptiness: by storing hashed fingerprints of length
$K \approx \log_2(\mathcal{L}/\varepsilon)$ instead of full keys, the space becomes
independent of the original key length~$|r|$.

\subsection{Complexity Summary}

\begin{itemize}
  \item \textbf{Build:} $O(n \cdot |r|)$ --- a single pass over sorted keys.
  \item \textbf{Query:} $O(|r|/w)$ expected (block index + binary search over ${\sim}2$
    keys of $|r|$ bits each); $O((|r|/w) \log n)$ worst case if all keys collide in a
    single block. When used inside ARE with $K$-bit fingerprints fitting in one machine
    word, this reduces to $O(1)$ expected.
  \item \textbf{Space:} $n \log_2(r/n) + O(n)$ bits, matching the information-theoretic
    lower bound.
\end{itemize}
